DATA 621 Homework #4

### 2019-11-29 final project/Manuscript.Rmd

---
title             : "A Logistic Regression Approach to CoIL Challenge 2000"
shorttitle        : " "
author: 
  - name          : "Corey Arnouts"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "119 W 31st St., New York, NY 10001"
    email         : "Corey.Arnouts@spsmail.cuny.edu"
  - name          : "Adam Douglas"
    affiliation   : "1"
  - name          : "Jason Givens-Doyle"
    affiliation   : "1"
  - name          : "Michael Silva"
    affiliation   : "1"
affiliation:
  - id            : "1"
    institution   : "MS in Data Science Students CUNY School of Professional Studies"
abstract: |
  A logistic regression based solution to the CoIL Challenge 2000 is described. The challenge consists of correctly identifying potential customers for an insurance product, and describing their characteristics.
  <!-- https://tinyurl.com/ybremelq 
    One sentence summarizing the main result (with the words "**here we show**" or their equivalent).

@@

  Two or three sentences to provide a **broader perspective**, readily comprehensible to a scientist in any discipline.
  -->
keywords          : "CoIL Challenge, Logistic Regression"
wordcount         : "X"
bibliography      : ["Manuscript.bib"]
floatsintext      : no
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : no
mask              : no
draft             : no
documentclass     : "apa6"
classoption       : "man"
output:
  papaja::apa6_pdf:
    #citation_package: natbib #biblatex
  html_document: default
---

```{r setup, include = FALSE}
# Documentation at https://crsh.github.io/papaja_man/
# If you have no use for TeX beyond rendering R Markdown documents, I recommend you use TinyTex.
# install.packages("tinytex")
# tinytex::install_tinytex()
if(!"papaja" %in% rownames(installed.packages())) devtools::install_github("crsh/papaja")
library("papaja")

library(tidyverse)

@@

```{r analysis-preferences}
# Seed for random number generation
set.seed(42)
knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
```

# Introduction
<!-- Describe the background and motivation of your problem.-->

@@

In total 147 participants registered and 43 submitted solutions [@Putten]. In this paper we set out to complete the first part of the COIL Challenge. **SUMARISE FINDINGS?**

@@

Participants used a variety of approaches in formulating their submissions including: Boosted Decision Tree [@McKone], Classification and Regressio Tree (CART) [@Simmonds], Classification Trees with Bagging [@White], C4.5 [@Rickets; @Seewald], Evolutionary Algorithm [@Koudijs], Fuzzy Classifier [@Abonyi; @Kaymak], Genetic Algorithms and Hill-climbers [@Carter], Inductive Learning by Logic Minimization (ILLM) [@Gamberger; @Smuc], Instance Based Reasoning (iBARET) [@Miksovsky], K-Means [@Vesanto], KXEN [@Bera], LOGIT [@Doornik], Mask Perceptron with Boosting [@Leckie], Midos Algorithm [@Krogel], N-Tuple Classifier [@Jorgensen], Naïve Bayes [@Elkan; @Kontkanen], Neural Networks[@Brierley; @Crocoll; @Kim; @Shtovba_Mashnitskiy], Phase Intervals and Genetic Algorithms [@Shtovba], Scoring System [@Lewandowski], Support Vector Machines[@Keerthi], and XCS [@Greenyer].

```{r}
# Recreate the chart found on page 2 of http://liacs.leidenuniv.nl/~puttenpwhvander/library/cc2000/PUTTEN~1.pdf
prediction_scores <- data.frame(score = c(38, 46, 53, 58, 65, 72, 74, 80, 83, 86, 91, 94, 95, 96, 97, 99, 101, 103, 104, 105, 106, 107, 108, 109, 110, 111, 112, 115, 121),
                                n = c(1, 1, 1, 1, 1, 1, 1, 1, 1, 2, 1, 1, 1, 3, 1, 2, 1, 1, 1, 3, 1, 2, 2, 4, 2, 2, 2, 1, 1))
ggplot(data=prediction_scores, aes(x=score, y=n)) +
  geom_bar(stat="identity") +
  xlab("Policy Owners") +
  ylab("Submissions") +
  xlim(37, 122) +
  ggtitle("Correct Predictions from CoIL 2000 Challenge Submissions")
```

The maximum number of policyowners that could be found was 238.  The submissions identified 95 policy owners on average.  The winning model [@Elkan] identified 121 policy owners.  Random selection results in identifying 42 policy owners. The standard benchmark tests result in 94 (k-nearest neighbor), 102 (naïve bayes), 105 (neural networks) and 118 (linear) policy owners. [@Putten].

Our investigation is similar to @Doornik in that we used a LOGIT model. **Reproduce his model and describe the results**

@@

# References
```{r create_references}
r_refs(file = "Manuscript.bib")
```

@@

# Appendices
<!--
- Supplemental tables and/or figures.
-->
## R statistical programming code.

<code>
```{r, null_prefix = TRUE, comment=NA}
conn <- file("CoIL.r", open="r")
lines <- readLines(conn)
for (i in 1:length(lines)){
  cat(lines[i], "\n")
}
close(conn)
```
</code>

>>>>

---
title             : "A Logistic Regression Approach to CoIL Challenge 2000"
shorttitle        : " "
author            : "Corey Arnouts, Adam Douglas, Jason Givens-Doyle, Michael Silva"
affiliation       : "MS in Data Science Students CUNY School of Professional Studies"
abstract: |
  A logistic regression based solution to the CoIL Challenge 2000 is described. The challenge consists of correctly identifying potential customers for an insurance product, and describing their characteristics.
  <!-- https://tinyurl.com/ybremelq 
    One sentence summarizing the main result (with the words "**here we show**" or their equivalent).

@@

  Two or three sentences to provide a **broader perspective**, readily comprehensible to a scientist in any discipline.
  -->
keywords          : "CoIL Challenge, Logistic Regression"
wordcount         : "X"
bibliography      : ["Manuscript.bib"]
floatsintext      : no
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : no
mask              : no
draft             : no
documentclass     : "apa6"
classoption       : "man"
output: 
  word_document:
    reference_docx: word-template.docx
  papaja::apa6_pdf:
    #citation_package: natbib #biblatex
  html_document: default
---

```{r setup, include = FALSE}
# Documentation at https://crsh.github.io/papaja_man/
# If you have no use for TeX beyond rendering R Markdown documents, I recommend you use TinyTex.
# install.packages("tinytex")
# tinytex::install_tinytex()
if(!"papaja" %in% rownames(installed.packages())) devtools::install_github("crsh/papaja")
library("papaja")
library(kableExtra)
library(tidyverse)
library(pander)

@@

```{r analysis-preferences, echo=FALSE}
# Seed for random number generation
set.seed(42)
knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
```

```{r data, echo=FALSE}
df <- read.delim("data/ticdata2000.txt", header = FALSE)
names(df) <- c("MOSTYPE", "MAANTHUI", "MGEMOMV", "MGEMLEEF", "MOSHOOFD",
               "MGODRK", "MGODPR", "MGODOV", "MGODGE", "MRELGE", "MRELSA",
               "MRELOV", "MFALLEEN", "MFGEKIND", "MFWEKIND", "MOPLHOOG",
               "MOPLMIDD", "MOPLLAAG", "MBERHOOG", "MBERZELF", "MBERBOER",
               "MBERMIDD", "MBERARBG", "MBERARBO", "MSKA", "MSKB1", "MSKB2",
               "MSKC", "MSKD", "MHHUUR", "MHKOOP", "MAUT1", "MAUT2", "MAUT0",
               "MZFONDS", "MZPART", "MINKM30", "MINK3045", "MINK4575",
               "MINK7512", "MINK123M", "MINKGEM", "MKOOPKLA", "PWAPART",
               "PWABEDR", "PWALAND", "PPERSAUT", "PBESAUT", "PMOTSCO",
               "PVRAAUT",  "PAANHANG", "PTRACTOR", "PWERKT", "PBROM", "PLEVEN",
               "PPERSONG", "PGEZONG", "PWAOREG", "PBRAND", "PZEILPL",
               "PPLEZIER", "PFIETS", "PINBOED", "PBYSTAND", "AWAPART",
               "AWABEDR", "AWALAND", "APERSAUT", "ABESAUT", "AMOTSCO",
               "AVRAAUT", "AAANHANG", "ATRACTOR", "AWERKT", "ABROM", "ALEVEN",
               "APERSONG", "AGEZONG", "AWAOREG",  "ABRAND", "AZEILPL",
               "APLEZIER", "AFIETS", "AINBOED", "ABYSTAND", "CARAVAN")
eval <- read.delim("data/ticeval2000.txt", header = FALSE)
temp <- read.delim("data/tictgts2000.txt", header = FALSE)
eval$CARAVAN <- temp$V1
names(eval) <- names(df)
```
# Introduction
<!-- Describe the background and motivation of your problem.-->

@@

```{r, echo=FALSE}
# Recreate the chart found on page 2 of http://liacs.leidenuniv.nl/~puttenpwhvander/library/cc2000/PUTTEN~1.pdf
prediction_scores <- data.frame(score = c(38, 46, 53, 58, 65, 72, 74, 80, 83, 86, 91, 94, 95, 96, 97, 99, 101, 103, 104, 105, 106, 107, 108, 109, 110, 111, 112, 115, 121),
                                n = c(1, 1, 1, 1, 1, 1, 1, 1, 1, 2, 1, 1, 1, 3, 1, 2, 1, 1, 1, 3, 1, 2, 2, 4, 2, 2, 2, 1, 1))
ggplot(data=prediction_scores, aes(x=score, y=n)) +
  geom_bar(stat="identity") +
  xlab("Number of Correct Predictions") +
  ylab("CoIL Challenge Submissions") +
  xlim(37, 122)
```

In total 147 participants registered and 43 submitted solutions [@Putten]. The maximum number of policyowners that could be found was 238.  The submissions identified 95 policy owners on average.  The winning model [@Elkan] identified 121 policy owners.  Random selection results in identifying 42 policy owners. The standard benchmark tests result in 94 (k-nearest neighbor), 102 (naïve bayes), 105 (neural networks) and 118 (linear) policy owners. [@Putten].

In this paper we set out to complete the first part of the COIL Challenge. <!--**SUMARISE FINDINGS?**-->

@@

Participants used a variety of approaches in formulating their submissions including: Boosted Decision Tree [@McKone], Classification and Regression Tree (CART) [@Simmonds], Classification Trees with Bagging [@White], C4.5 [@Rickets; @Seewald], Evolutionary Algorithm [@Koudijs], Fuzzy Classifier [@Abonyi; @Kaymak], Genetic Algorithms and Hill-climbers [@Carter], Inductive Learning by Logic Minimization (ILLM) [@Gamberger; @Smuc], Instance Based Reasoning (iBARET) [@Miksovsky], K-Means [@Vesanto], KXEN [@Bera], LOGIT [@Doornik], Mask Perceptron with Boosting [@Leckie], Midos Algorithm [@Krogel], N-Tuple Classifier [@Jorgensen], Naïve Bayes [@Elkan; @Kontkanen], Neural Networks[@Brierley; @Crocoll; @Kim; @Shtovba_Mashnitskiy], Phase Intervals and Genetic Algorithms [@Shtovba], Scoring System [@Lewandowski], Support Vector Machines[@Keerthi], and XCS [@Greenyer].

<!--Our investigation is similar to @Doornik in that we used a LOGIT model. **Reproduce his model and describe the results**-->

```{r, echo=FALSE}
doornik <- function(df){
  df <- df %>%
    mutate(PBRAND_2_or_6 = ifelse(PBRAND == 2 | PBRAND == 6, 1, 0),
           PBRAND_3_or_4 = ifelse(PBRAND == 3 | PBRAND == 4, 1, 0),
           PPLEZIER_gt_0 = ifelse(PPLEZIER > 0, 1, 0),
           PPERSAUT_6 = ifelse(PPERSAUT == 6, 1, 0))
  z <- -4.1 - (0.13 * df$MOPLLAAG) - (0.3 * df$MINK123M) + (0.17 * df$MINKGEM) + (0.54 * (df$ALEVEN + df$AFIETS + df$ABYSTAND)) - df$PBRAND_2_or_6 + (0.8 * df$PBRAND_3_or_4) + (2.4 * df$PPLEZIER_gt_0) + (1.5 * df$PPERSAUT_6) + (0.28 * (df$PWAOREG - df$PLEVEN))
  p_caravan <- exp(z) / (1 + exp(z))
  #p_caravan
  ifelse(p_caravan > 0.5, 1, 0)
}

eval$doornik <- doornik(eval)
```

@@

# References
```{r create_references, echo=FALSE}
r_refs(file = "Manuscript.bib")
```

@@

# Appendices

<!--
- Supplemental tables and/or figures.
-->

## Data Dictionary

```{r, results='asis', echo=FALSE}
data_dictionary <- data.frame(
  Name=c("MOSTYPE", "MAANTHUI", "MGEMOMV", "MGEMLEEF", "MOSHOOFD", "MGODRK", "MGODPR", "MGODOV", "MGODGE", "MRELGE", "MRELSA", "MRELOV", "MFALLEEN", "MFGEKIND", "MFWEKIND", "MOPLHOOG", "MOPLMIDD", "MOPLLAAG", "MBERHOOG", "MBERZELF", "MBERBOER", "MBERMIDD", "MBERARBG", "MBERARBO", "MSKA", "MSKB1", "MSKB2", "MSKC", "MSKD", "MHHUUR", "MHKOOP", "MAUT1", "MAUT2", "MAUT0", "MZFONDS", "MZPART", "MINKM30", "MINK3045", "MINK4575", "MINK7512", "MINK123M", "MINKGEM", "MKOOPKLA", "PWAPART", "PWABEDR", "PWAAND", "PPERSAUT", "PBESAUT", "PMOTSCO", "PVRAAUT", "PAANHANG", "PTRACTOR", "PWERKT", "PBROM", "PLEVEN", "PPERSONG", "PGEZONG", "PWAOREG", "PBRAND", "PZEILPL", "PPLEZIER", "PFIETS", "PINBOED", "PBYSTAND", "AWAPART", "AWABEDR", "AWALAND", "APERSAUT", "ABESAUT", "AMOTSCO", "AVRAAUT", "AAANHANG", "ATRACTOR", "AWERKT", "ABROM", "ALEVEN", "APERSONG", "AGEZONG", "AWAOREG", "ABRAND", "AZEILPL", "APLEZIER", "AFIETS", "AINBOED", "ABYSTAND", "CARAVAN"),
  Description = c("Customer Subtype", "Number of houses", "Avg size household", "Avg age", "Customer main type", "Roman catholic", "Protestant", "Other religion", "No religion", "Married", "Living together", "Other relation", "Singles", "Household without children", "Household with children", "High level education", "Medium level education", "Lower level education", "High status", "Entrepreneur", "Farmer", "Middle management", "Skilled labourers", "Unskilled labourers", "Social class A", "Social class B1", "Social class B2", "Social class C", "Social class D", "Rented house", "Home owners", "1 car", "2 cars", "No car", "National Health Service", "Private health insurance", "Income < 30.000", "Income 30-45.000", "Income 45-75.000", "Income 75-122.000", "Income >123.000", "Average income", "Purchasing power class", "Contribution private third party insurance", "Contribution third party insurance (firms)", "Contribution third party insurane (agriculture)", "Contribution car policies", "Contribution delivery van policies", "Contribution motorcycle/scooter policies", "Contribution lorry policies", "Contribution trailer policies", "Contribution tractor policies", "Contribution agricultural machines policies", "Contribution moped policies", "Contribution life insurances", "Contribution private accident insurance policies", "Contribution family accidents insurance policies", "Contribution disability insurance policies", "Contribution fire policies", "Contribution surfboard policies", "Contribution boat policies", "Contribution bicycle policies", "Contribution property insurance policies", "Contribution social security insurance policies", "Number of private third party insurance", "Number of third party insurance (firms)", "Number of third party insurane (agriculture)", "Number of car policies", "Number of delivery van policies", "Number of motorcycle/scooter policies", "Number of lorry policies", "Number of trailer policies", "Number of tractor policies", "Number of agricultural machines policies", "Number of moped policies", "Number of life insurances", "Number of private accident insurance policies", "Number of family accidents insurance policies", "Number of disability insurance policies", "Number of fire policies", "Number of surfboard policies", "Number of boat policies", "Number of bicycle policies", "Number of property insurance policies", "Number of social security insurance policies", "Number of mobile home policy"))
pander(data_dictionary)
```

## R statistical programming code.

<code>
```{r, null_prefix = TRUE, comment=NA, echo=FALSE}
conn <- file("CoIL.r", open="r")
lines <- readLines(conn)
for (i in 1:length(lines)){
  cat(lines[i], "\n")
}
close(conn)
```
</code>

### 2019-11-29 hw4/HW4_Mike.Rmd

```{r}
df <- df %>% 
   mutate_at(vars(c("CAR_AGE", "YOJ", "AGE", "INCOME", "HOME_VAL")), ~ifelse(is.na(.), median(., na.rm = TRUE), .))
```

@@

create_features <- function(d){
  d %>%
    mutate(LOG_INCOME = log(INCOME + 1),
           LOG_HOME_VAL = log(HOME_VAL + 1),
           AVG_CLAIM = ifelse(CLM_FREQ > 0, OLDCLAIM / CLM_FREQ, 0),
           PRIOR_ACCIDENT = factor(ifelse(OLDCLAIM == 0 & AVG_CLAIM == 0, 0, 1)),
           COLLEGE_EDUCATED = factor(ifelse(EDUCATION %in% c("Bachelors", "Masters", "PhD"), 1, 0)),
           URBAN_DRIVER = factor(ifelse(URBANICITY == "Highly Urban/ Urban", 1, 0)),
           YOUNG_MALE = factor(ifelse(SEX == "M" & AGE < 25, 1, 0)),
           YOUNG = factor(ifelse(AGE < 25, 1, 0)),
           RED_SPORTS_CAR = factor(ifelse(CAR_TYPE == "Sports Car" & RED_CAR == "yes", 1, 0)),
           HAS_KIDS = factor(ifelse(HOMEKIDS == 0, 0, 1)),
           KID_DRIVERS = factor(ifelse(KIDSDRIV == 0, 0, 1)),
           TARGET_AMT_OUTLIER = ifelse(TARGET_AMT < outlier, 0, 1)) %>%
    select(-URBANICITY)
}

@@

@@

@@

```{r}
temp <- data.frame(yhat = predict(outlier_lm, amt_test), actual = amt_test$TARGET_AMT, TARGET_AMT_OUTLIER = amt_test$TARGET_AMT_OUTLIER) 
temp %>%
  ggplot(., aes(actual, yhat, color=as.factor(TARGET_AMT_OUTLIER))) +
  geom_point() +
  scale_color_brewer(palette="Set1") +
  theme_light() +
  theme(legend.position = "none") 
```

```{r}
temp %>%
  mutate(error = yhat - actual) %>%
  mutate(`error %` = (error / actual)*100) %>%
  group_by(TARGET_AMT_OUTLIER) %>%
  summarise(error = mean(error),
            `error %` = mean(`error %`)) %>%
  kable() %>%
  kable_styling()
```

It understates the claim prediciton by about $95 for the small claims and $1,100 for the large claims.  The error on the is about 55% of the estimate for the small claims and 31% for the large claims.  In summary it is roughly right.  It would preform a lot better than the baseline model.  The table below offers the similar metrics:

```{r}
data.frame(yhat = predict(baseline_lm, amt_test), actual = amt_test$TARGET_AMT, TARGET_AMT_OUTLIER = amt_test$TARGET_AMT_OUTLIER) %>%
  mutate(error = yhat - actual) %>%
  mutate(`error %` = (error / actual)*100) %>%
  group_by(TARGET_AMT_OUTLIER) %>%
  summarise(error = mean(error),
            `error %` = mean(`error %`)) %>%
  kable() %>%
  kable_styling()
```

The challenge will be to create a classifier.  There are `r nrow(amt_train[amt_train$TARGET_AMT_OUTLIER == 1,])` out of `r nrow(amt_train)` that are outliers.  Let's create another balanced data set and see if we can build a classifier.

@@

```{r}
over_sample_train_2 %>%
  keep(is.numeric)%>%
  select(-TARGET_AMT_OUTLIER, -INDEX, -TARGET_AMT) %>%
  cor(., over_sample_train_2$TARGET_AMT_OUTLIER) %>%
  kable() %>%
  kable_styling()
```

@@

```{r, null_prefix = TRUE, comment=NA}
outlier_model <- glm(TARGET_AMT_OUTLIER ~ BLUEBOOK + MVR_PTS + JOB, family = binomial(link = "logit"), over_sample_train_2)
summary(outlier_model)
outlier_model_results <- evaluate_model(outlier_model, test, "TARGET_AMT_OUTLIER", 0.5)
```

#### Rural Model
```{r}
M <- train %>%
  filter(TARGET_FLAG == 1) %>%
  filter(URBAN_DRIVER == 0) %>%
  purrr::keep(is.numeric) %>%
  na.omit() %>%
  cor(.)
corrplot(M, type = "upper")
```

```{r}
rural_fit <- train %>%
  filter(TARGET_FLAG == 1) %>%
  filter(URBAN_DRIVER == 0) %>%
  lm(TARGET_AMT ~ BLUEBOOK + CAR_AGE + TRAVTIME, .)
summary(rural_fit)
```

#### Urban Model

```{r}
M <- train %>%
  filter(TARGET_FLAG == 1) %>%
  filter(URBAN_DRIVER == 1) %>%
  purrr::keep(is.numeric) %>%
  na.omit() %>%
  cor(.)
corrplot(M, type = "upper")
```

```{r}
urban_fit <- train %>%
  filter(TARGET_FLAG == 1) %>%
  filter(URBAN_DRIVER == 1) %>%
  lm(TARGET_AMT ~ BLUEBOOK, .)
summary(urban_fit)
```

```{r}
temp <- over_sample_train_2 %>%
  select(-TARGET_FLAG, - TARGET_AMT)
fft <- FFTrees(TARGET_AMT_OUTLIER~., temp)
fft
```

@@

```{r}
predictions <- function(df, classifier, linear_model_1, linear_model_2){
  df$TARGET_FLAG <- ifelse(predict.glm(classifier, df, "response") >= 0.5, 1, 0)
  # We assume that everyone with a TARGET_FLAG = 0 has a TARGET_AMT as zero.  
  # We then refine it with the two linear models
  df$model_1_yhat <- predict(linear_model_1, df)
  df$model_2_yhat <- predict(linear_model_2, df)
  df <- df %>%
    mutate(TARGET_AMT = ifelse(URBAN_DRIVER == 1, model_1_yhat, model_2_yhat)) %>%
    mutate(TARGET_AMT = ifelse(TARGET_FLAG == 0, 0, TARGET_AMT))
  return(df)
}

evaluation <- predictions(evaluation, model, urban_fit, rural_fit)
```

>>>>

```{r}
fix_missing <- function(df) {
  df %>% 
    mutate_at(vars(c("CAR_AGE", "YOJ", "AGE", "INCOME", "HOME_VAL")), ~ifelse(is.na(.), median(., na.rm = TRUE), .))
}

df <- fix_missing(df)
evaluation <- fix_missing(evaluation)
```

@@

create_features <- function(d){
  d %>%
    mutate(LOG_INCOME = log(INCOME + 1),
           LOG_HOME_VAL = log(HOME_VAL + 1),
           AVG_CLAIM = ifelse(CLM_FREQ > 0, OLDCLAIM / CLM_FREQ, 0),
           PRIOR_ACCIDENT = factor(ifelse(OLDCLAIM == 0 & AVG_CLAIM == 0, 0, 1)),
           COLLEGE_EDUCATED = factor(ifelse(EDUCATION %in% c("Bachelors", "Masters", "PhD"), 1, 0)),
           URBAN_DRIVER = factor(ifelse(URBANICITY == "Highly Urban/ Urban", 1, 0)),
           YOUNG_MALE = factor(ifelse(SEX == "M" & AGE < 25, 1, 0)),
           YOUNG = factor(ifelse(AGE < 25, 1, 0)),
           STUDENT = factor(ifelse(JOB == "Student", 1, 0)),
           MVR_PTS_GT_0 = factor(ifelse(MVR_PTS > 0, 1, 0)),
           RED_SPORTS_CAR = factor(ifelse(CAR_TYPE == "Sports Car" & RED_CAR == "yes", 1, 0)),
           HAS_KIDS = factor(ifelse(HOMEKIDS == 0, 0, 1)),
           KID_DRIVERS = factor(ifelse(KIDSDRIV == 0, 0, 1)),
           TARGET_AMT_OUTLIER = ifelse(TARGET_AMT < outlier, 0, 1)) %>%
    select(-URBANICITY)
}

@@

By simply using the median to predict the values of the claims we would underestimate the actual value on average by $1,600 dollars.  On a percentage basis the error would be 50% of the actual.

@@

Well the average error has decreased which is good but the average error share of the actual has doubled.  This is a garbage model.

@@

The predictions on average understate the actual value by $140.  The error as a percent of the actual is close to what we get with just using the median.  The improvement really comes from using a higher value to estimate the claim for the outliers.

The challenge will be to create a classifier.  There are `r nrow(amt_train[amt_train$TARGET_AMT_OUTLIER == 1,])` out of `r nrow(amt_train)` that are outliers.  Let's create another balanced data set and see if we can build another classifier.

@@

```{r eval=FALSE, echo=FALSE}
over_sample_train_2 %>%
  keep(is.numeric)%>%
  select(-TARGET_AMT_OUTLIER, -INDEX, -TARGET_AMT) %>%
  cor(., over_sample_train_2$TARGET_AMT_OUTLIER) %>%
  kable() %>%
  kable_styling()
```

@@

It looks like the `BLUEBOOK` and `PARENT1` are the only variables that are correlated with this outcome.  So let's build the classifier.

```{r, null_prefix = TRUE, comment=NA}
outlier_model <- glm(TARGET_AMT_OUTLIER ~ BLUEBOOK + PARENT1, family = binomial(link = "logit"), over_sample_train_2)
summary(outlier_model)
outlier_model_results <- evaluate_model(outlier_model, test, "TARGET_AMT_OUTLIER")
```

Now to test this out.  Based on our linear regression test set we will predict if the observation is likely to be an outlier or not.  We will then estimate the `TARGET_AMT` using the linear model.  We will then evaluate the results of the "model".

```{r}
temp <- amt_test
temp$TARGET_AMT_OUTLIER <- ifelse(predict.glm(outlier_model, amt_test, "response") >= 0.5, 1, 0)
temp$TARGET_AMT_yhat <- predict(outlier_lm, amt_test)
evaluate_lm(temp$TARGET_AMT_yhat, temp$TARGET_AMT)
```

So through this somewhat convoluted approach we have done slightly better than using the median.

@@

The final predictions will use the alternative traditional model to predict the `TARGET_FLAG` variable, then pass it through the second classifier which predicts the `TARGET_AMT_OUTLIER` flag.  We then use the linear model to make the final amount prediction.

```{r}
predictions <- function(df, classifier_1, linear_model, classifier_2){
  df$TARGET_FLAG <- ifelse(predict.glm(classifier_1, df, "response") >= 0.5, 1, 0)
  # We assume that everyone with a TARGET_FLAG = 0 has a TARGET_AMT as zero.  
  # We then refine it with the outlier model.
  df$TARGET_AMT_OUTLIER <- ifelse(predict.glm(classifier_2, df, "response") >= 0.5, 1, 0)
  df$yhat <- predict(linear_model, df)
  df <- df %>%
    mutate(TARGET_AMT = ifelse(TARGET_AMT_OUTLIER == 1, yhat, 0)) %>%
    mutate(TARGET_AMT = ifelse(TARGET_FLAG == 0, 0, TARGET_AMT)) %>%
    select(-yhat, -TARGET_AMT_OUTLIER)
  return(df)
}

evaluation <- predictions(evaluation, model, outlier_lm, outlier_model)
```
